\sysfull

### 2017-11-17 paper/coalescing.tex
coalescing: whitespace fix
coalescing and evaluation revision

\textbf{Task Coalescing Strategies.}

The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime.
%
The general structure of our strategies is to increase the target task size by
some positive delta $C_\text{up}$ after the dynamic coalesced task completes,
and decrease it by some negative delta $C_\text{down}$ upon a reboot after a
power failure.
%
The choice of $C_\text{up}$ and $C_\text{down}$, including their units, defines
the strategy and its performance.
%
For example, a naive strategy that fixes $C_\text{up}$ and $C_\text{down}$ to
``one static task``, will be very slow to react to changes in incoming energy,
since its dynamic task size can only change by the size of one (small) static
task per charge-discharge cycle.
%
Working from these observations, we propose and evaluate two coalescing
strategies for \sys: \textbf{History-aware Coalescing (HC)} and
\textbf{Task-size- and History-aware Coalescing (TSHC)}.

@@

\todo{clarify}{AC}
With this strategy \sys calculates only one parameter $C=C_U=C_D$ based on the number of tasks completed, until $t$th task commit, $S_t$, during the current operational period. \sys begins execution in a coalesced task with $S_t=0$. When $S_t=C_{t-1}-1$ coalesced tasks have been executed without power interrupt (where $C_{t-1}$ defines $C$ until $t-1$ task commit) a task commit follows. After each commit, \sys assigns new coalescing factor as $C_{t}=\lceil \sum_{k=1}^{t}S_{k-1}/2\rceil$. This implies that if more tasks complete in an operating period, \sys attempts to coalesce more tasks. However, tasks coalescing are increased by a half the speed of the successful task completion. This way we adapt to the coalescing speed/wasted effort trade-off: at the potential power interrupt \sys does not immediately reduce coalescing factor to one, and with successful page commit of coalescing task, \sys gradually increases coalescing factor. In both cases \sys reduces the effect of outliers, i.e. short bursts of energy or short bursts of frequent power interrupts.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/TskDist.pdf}%coalescing_timeline
	\caption{\textbf{Distribution of task sizes, estimated by task execution times.} The
wide variation in task size motivates accounting for task size in the coalescing strategy.
\todo{Describe X axis, no capitals in titles - except first word; markers in addition to colors per app; remove 4.7}{Amjad}}
	\label{fig:task_profiling}
\end{figure}

>>>>

\textbf{Task Coalescing Strategies.} 
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime.
%
The general structure of our strategies is to increase the target task size by
some positive delta $C_\text{up}$ after the dynamic coalesced task completes,
and decrease it by some negative delta $C_\text{down}$ upon a reboot after a
power failure.
%
The choice of $C_\text{up}$ and $C_\text{down}$, including their units, defines
the strategy and its performance.
%
For example, a naive strategy that fixes $C_\text{up}$ and $C_\text{down}$ to
``one static task``, will be very slow to react to changes in incoming energy,
since its dynamic task size can only change by the size of one (small) static
task per charge-discharge cycle.
%
Working from these observations, we propose and evaluate two coalescing
strategies for \sys: \textbf{History-aware Coalescing (HC)} and
\textbf{Task-size- and History-aware Coalescing (TSHC)}.

@@

\todo{clarify}{AC}
With this strategy \sys calculates only one parameter $C=C_\text{up}=C_\text{down}$ based on the number of tasks completed, until $t$th task commit, $S_t$, during the current operational period. \sys begins execution in a coalesced task with $S_t=0$. When $S_t=C_{t-1}-1$ coalesced tasks have been executed without power interrupt (where $C_{t-1}$ defines $C$ until $t-1$ task commit) a task commit follows. After each commit, \sys assigns new coalescing factor as $C_{t}=\lceil \sum_{k=1}^{t}S_{k-1}/2\rceil$. This implies that if more tasks complete in an operating period, \sys attempts to coalesce more tasks. However, tasks coalescing are increased by a half the speed of the successful task completion. This way we adapt to the coalescing speed/wasted effort trade-off: at the potential power interrupt \sys does not immediately reduce coalescing factor to one, and with successful page commit of coalescing task, \sys gradually increases coalescing factor. In both cases \sys reduces the effect of outliers, i.e. short bursts of energy or short bursts of frequent power interrupts.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/TskDist.pdf}%coalescing_timeline
	\caption{\textbf{Distribution of task sizes, estimated by task execution times.} The wide variation in task size motivates accounting for task size in the coalescing strategy.}
	\label{fig:task_profiling}
\end{figure}
